\makeexperience{
    \job{Synx Games}{https://synx.games/}
    {Lincoln, UK}
    {Software Engineer (Internship)}
    {Feb 2025}{Present}
    {
        \item Co-led the end-to-end development of a multiplayer Roblox game from scratch, delivering a functional MVP in 8 weeks with core gameplay systems and UI built in TypeScript, React, and the Knit framework.\vspace{-0.5mm}
        \item Drove the development of a £500,000 Roblox Creator Fund application, creating pitch materials, timelines, and milestone plans to showcase long-term viability, player retention, and monetisation strategy.\vspace{-0.5mm}
        \item Established and managed an Agile workflow --- implementing a kanban board, scoped tickets, and structured \\sprints --- for focused delivery in a 2-person team, resulting in timely milestone delivery.
    }

    \job{B-Hive Innovations}{https://www.b-hiveinnovations.co.uk/}
    {Lincoln, UK}
    {Software \& Data Technician (Contract)}
    {May 2024}{Sept 2024}
    {
        \item Diagnosed and resolved 8 critical reliability issues in Python-based applications for the TuberScan Venture project, improving data accuracy by 30\% and ensuring accurate data collection for training machine-learning models.\vspace{-0.5mm}
        \item Enhanced data collection processes by automating data processing and validation pipelines, reducing manual \\errors to 0 and saving up to 5 hours of work per week spent fixing errors.\vspace{-0.5mm}
        \item Collaborated in an Agile, Scrum-based environment with a team of 8, using kanban for task tracking and Git for version control to improve productivity, meeting over 95\% of sprint objectives.
    }

    \job{Dollar Jeans}{https://www.dollarjeans.co.uk/}
    {Lincoln, UK}
    {E-Commerce Automation Engineer}
    {Jan 2023}{Mar 2024}
    {
        \item Managed an SQL database of 15,000+ products across eBay, Amazon, and Shopify, automating inventory updates \\for seamless synchronisation across platforms and generation of sales analytics for business insights.\vspace{-0.5mm}
        \item Optimised the product listing process by creating a Python script to automate generation of product descriptions, reducing average listing time by 50\% and saving up to 8 hours of work per week.
    }
}