\makeprojects{
    %\project{Open-Licence Media Web App}
    %{}
    %{Feb 2025}{Present}
    %{https://github.com/alfieatkinson/open-licence-media-web-app}
    %{

    %}

    % \project{Personal Portfolio Website}
    % {Front-End Development (TypeScript, React, Next.js)}
    % {Jan 2025}{Present}
    % {https://github.com/alfieatkinson/portfolio}
    % {
    %     \item Developed a responsive portfolio website using React and TypeScript, achieving 1.29s First Contentful Paint, \\1.64s Largest Contentful Paint, and 8ms Interaction to Next Paint through Vite-based performance optimisation.\vspace{-0.5mm}
    %     \item Migrated from a Vite static build to Next.js server-side rendering, slashing Cumulative Layout Shift from 0.46 to \\0.001 and Time to First Byte from 2.4s to 0.13s, achieving a consistent 93--97 Vercel `Real Experience Score'.
    % }

    \project{OpenGalaxy}
    {Full-Stack Development (TypeScript, React, Next.js, Tailwind CSS, Django, PostgreSQL)}
    {Jan 2025}{May 2025}
    {https://github.com/alfieatkinson/opengalaxy}
    {https://opengalaxy.alfieatkinson.dev}
    {
        \item Engineered a high-performance React and Next.js SPA using TypeScript, reducing runtime errors with static typing, and hybrid CSR/SSR rendering, resulting in a 25\% faster page load and improved SEO rankings.\vspace{-0.5mm}
        \item Implemented responsive UI components with TailwindCSS and DaisyUI, cutting DOM size by 80\% and accelerating styling workflows, reducing frontend maintenance time by 60\% compared to standard CSS.\vspace{-0.5mm}
        \item Designed backend data schema with Django and PostgreSQL fully normalised to 3NF, optimising query efficiency \\and data integrity for user accounts and media metadata, reducing redundant storage by 15\%.\vspace{-0.5mm}
        \item Secured user authentication using Django REST Framework with HttpOnly JWT tokens, preventing client-side \\script access and mitigating XSS risks, achieving robust security for sensitive user sessions.\vspace{-0.5mm}
        \item Automated full-stack CI/CD pipelines integrating Vercel (frontend) and Heroku (backend), with GitHub Actions enforcing Cypress E2E tests on all PRs, decreasing deployment failures by 35\% and accelerating release cycles.
    }

    \project{Library Management System}
    {Systems Programming (C++, JSON, Networking, Multi-threading)}
    {Oct 2024}{Jan 2025}
    {https://github.com/alfieatkinson/library-management-system}
    {}
    {
        \item Engineered a library management system CLI in C++ with CRUD operations and JSON data persistence.\vspace{-0.5mm}
        \item Implemented 40+ unit tests using Catch2 to facilitate continuous integration and Test-Driven Development.\vspace{-0.5mm}
        \item Integrated multi-threading and socket-based networking, enabling concurrent user interactions and remote access.
    }

    \project{Sentiment Analysis Tool (B.Sc. Dissertation Project)}
    {Data Science / Machine Learning (Python, NLP, TensorFlow)}
    {Sept 2023}{May 2024}
    {https://github.com/alfieatkinson/sentiment-analysis-tool}
    {}
    {
        \item Designed and implemented a sentiment analysis tool in Python leveraging BERT for social media analytics, \\delivering sentiment predictions with 86.95\% accuracy, furthering to 95\% with k-fold cross-validation enabled.\vspace{-0.5mm}
        \item Optimised data pipelines with Pandas and NumPy, improving processing speed by up to 80\% on large datasets.
    }
}
